Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-14 ipsj/paper.tex
Add Related Work

>>>>

To develop the software of IoT systems, several approaches have been proposed \cite{par:frameworkCPS} such as General-purpose Programming Languages (GPLs), Wireless Sensor Network (WSN) macroprogramming, Cloud-based platforms, and Model-Driven Development (MDD).

The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.

WSN macroprogramming provides abstractions to specify high-level collaborative behaviors, while hiding low-level details such as message passing and state maintenance.
nesC, a programming language used to build applications for the TinyOS platform \cite{par:nesc}, has been proposed.
nesC/TinyOS is designed for WSN nodes with limited resources e.g., 8 kilobytes of program memory, 512 bytes of RAM, but not supported TCP/IP implementation.

Cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop).
In addition, it offers the ease deployment and evolution because the application logic is centrally located in a cloud platform.
However, it is platform-dependent design, and restricts developers in terms of functionality such as in-network aggregation or direct node-to-node communication locally.

To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
MDD provides the benefits of re-usable, platform-independent, extensible design, however it needs long development time to build a MDD system.
